%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Current Research Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------	
\cventry
{PI: Prof. Q. Nie, University of California, Irvine} % Job title
{High-Order Adaptive Methods for Stochastic ODEs} % Organization
{Numerical SODEs} % Location
{2014-Present} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Utilizing high-order Stochastic Runge-Kutta methods for SODEs to develop adaptive SODE methods.}
		\item {Investigating the statistics of the Brownian Bridge to apply arbitrary time steps.}
		\item {Implementing the solutions as high-performance open source packages.}
	\end{cvitems}
}
	
%---------------------------------------------------------	
\cventry
{PI: Prof. Q. Nie, University of California, Irvine} % Job title
{Machine Learning for the Optimization Numerical Methods for Stochastic ODEs} % Organization
{Numerical SODEs} % Location
{2014-Present} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Analyzing the mathematical problem from an experimental viewpoint and applying scientific methods.}
		\item {Implementing machine learning methods to optimize the numerical methods for various properties.}
		\item {Identifying computationally-efficient high-order implicit methods.}
	\end{cvitems}
}

%---------------------------------------------------------
\cventry
	{PIs: Prof. Q. Nie and Prof. T. Schilling, University of California, Irvine} % Job title
	{Neural Crest Migration Patterns in Craniofacial Development} % Organization
	{Systems Developmental Biology} % Location
	{2013-Present} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Utilizing confocal microscopy to image the migration and cell-fate decisions of neural crest cells.}
			\item {Quantifying the outcomes of hypotheses via SDE models}
		\end{cvitems}
	}
	
%---------------------------------------------------------
\cventry
	{PI: Prof. Q. Nie, University of California, Irvine} % Job title
	{Mechanisms for Control of Variability in Biological Organisms} % Organization
	{Mathematical Biology} % Location
	{2013-Present} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Developed phenomenological (S)PDE models of retinoic acid signaling pathways of zebrafish.}
			\item {Identified network motifs which are used to attenuate the noise in the response signal.}
		\end{cvitems}
	}
		
%---------------------------------------------------------
\cventry
	{PI: Prof. J. Rowsell, Oberlin College} % Job title
	{Detection of Superspace Symmetry in Incommensurate Crystallography} % Organization
	{Crystallography} % Location
	{2013-Present} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Solved for and refined crystal structure from crystallography experiments using SHELX and Jana2006.}
			\item {First reported structure of “H-Acid”, a commodity dye intermediate in heavy use since 1890.}
		\end{cvitems}
	}
	
%---------------------------------------------------------
\end{cventries}
%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Research in Industrial Projects for Students (RIPS-HK)} % Job title
    {Project Manager, Baidu, Inc.} % Organization
    {Hong Kong, China} % Location
    {Summer 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Lead an international team of researchers on a mathematical/computational research project for Baidu, Inc.}
        \item {Developed new algorithms for movie recommendation utilizing machine learning techniques.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Oberlin College Department of Chemistry and Biochemistry} % Job title
    {Research Assistant} % Organization
    {Oberlin, Ohio} % Location
    {2012-2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Modeled incommensurate crystal structures using x-ray diffraction data from crystallography experiments.}
        \item {Solved for the modulated structure for low temperature crystals of “H-Acid”, a commodity dye intermediate.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Oberlin College Residential Education} % Job title
    {Web Developer} % Organization
    {Oberlin, Ohio} % Location
    {2009 - 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created and maintained secure web forms and programs in PHP and Perl.}
        \item {Developed the associated MYSQL relational databases for the housing data.}
        \item {Wrote scripts to convert housing data into interactive Excel sheets for use by non-programmers.}
      \end{cvitems} 
    }

%---------------------------------------------------------
  \cventry
    {Freelance} % Job title
    {Web Developer} % Organization
    {Oberlin, Ohio} % Location
    {2009 - 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created and maintained websites for professors and businesses.}
        \item {Scripted interfaces to ensure that information could be updated by individuals without programming experience.}
        \item {Examples: Fernando Gomez Herrero’s personal page (fernandogomezherrero.com), Acoustik Musik LTD.
        	(acoustikmusik.com), and my personal page (chrisrackauckas.com).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Oberlin Modeling Initiative} % Job title
    {Model Developer and Technical Assistant} % Organization
    {Oberlin, Ohio} % Location
    {2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed computational models for the Nova 2 Model Library and for classroom use.}
        \item {Wrote tutorials detailing how to script models using NovaScript.}
        \item {Created the World library for agent-based modeling in Nova.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
  {Oberlin College Mathematics Department} % Job title
  {Calculus Tutor} % Organization
  {Oberlin, Ohio} % Location
  {2009-2010} % Date(s)
  {
  	\begin{cvitems} % Description(s) of tasks/responsibilities
  		\item {Responsibilities included teaching Oberlin College students first and second semester calculus.}
  	\end{cvitems}
  }
  
  %---------------------------------------------------------
  
\cventry
    {Oberlin College and Mission Viejo High School Theater} % Job title
    {Lighting/Sound Technician} % Organization
    {Oberlin, Ohio / Mission Viejo, CA} % Location
    {2008-2010} % Date(s)
    {
    	\begin{cvitems} % Description(s) of tasks/responsibilities
    		\item {Designed and implemented lighting and sound for musical theater performances, dance showcases, and plays.}
    		\item {Maintained technical equipment, utilized digital signal processing for sound design, and built sets.}
    	\end{cvitems}
    }
    
    %---------------------------------------------------------
\end{cventries}
